Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-06 draft.tex
table references updates
add auc metrics and roc curve figures

			\centering\scriptsize
			\begin{tabular}{c | c | c | c | c}
				Terminus & Features & Training & Accuracy & EER \\

@@

				Simple & standard & until 3474 & 95.02\% & 0.03702 \\
				3 hidden layers & standard & until 10000 & 96.27\% & 0.03214 \\
				Simple & standard & until 23833 2 epochs & 90.07\% & 0.90069 \\
				Simple & standard & until 10000 2 epochs & 94.43\% & 0.04408 \\
				Simple & standard & until 10000 & 94.28\% & 0.04840 \\
				3 convolutional layers & standard & until 10000 & 62.80\% & 0.37198 \\
				Simple & expand pitch\-flucs & until 10000 & 93.31\% & 0.05661 \\
				3 hidden layers & expand pitch\-flucs & until 10000 & 93.87\% & 0.05317

@@

@@

			pitch fluctuation features and a complex terminus}

@@

		summarized by the feature is presented in tables \ref{table:exp-results-cterm} and
		\ref{table:exp-results-more-pitch-flucs}. 

>>>>

			\centering\tiny
			\begin{tabular}{c | c | c | c | c | c}
				Terminus & Features & Training & Accuracy & EER & AUC \\

@@

				Simple & standard & until 3474 & 95.02\% & 0.03702 & 0.90297 \\
				3 hidden layers & standard & until 10000 & 96.27\% & 0.03214 & 0.81763 \\
				Simple & standard & until 23833 2 epochs & 90.07\% & 0.90069 & 0.78889 \\
				Simple & standard & until 10000 2 epochs & 94.43\% & 0.04408 & 0.89445 \\
				Simple & standard & until 10000 & 94.28\% & 0.04840 & 0.90182 \\
				3 convolutional layers & standard & until 10000 & 62.80\% & 0.37198 & 0.50051 \\
				Simple & expand pitch\-flucs & until 10000 & 93.31\% & 0.05661 & 0.92727 \\
				3 hidden layers & expand pitch\-flucs & until 10000 & 93.87\% & 0.05317 & 0.83263

@@

			\includegraphics[width=0.7\textwidth]{images/roc_cterm.png}
			\caption{ROC curve of the best-performing model, with 3 hidden layers in the terminus and that standard feature set.}
			\label{fig:roc_cterm}
			\includegraphics[width=0.7\textwidth]{images/roc_mpf.png}
			\caption{ROC curve of the model with expanded pitch fluctuation features.}
			\label{fig:roc_mpf}
			\includegraphics[width=0.7\textwidth]{images/roc_mpf_cterm.png}
			\caption{ROC curve of the model with expanded pitch fluctuation features and a terminus with three hidden layers.}
			\label{fig:roc_mpf_cterm}

@@

			pitch fluctuation features and a terminus with three hidden layers}

@@

		summarized by the feature is presented in tables \ref{table:exp-results-cterm},
		\ref{table:exp-results-more-pitch-flucs} and \ref{table:exp-results-mpf-cterm}. 
